---
title: "W3 Reflection Excercise"
author: 
  - W3 Group 29
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "Analysis of Marriages in Toronto"
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

```


# Introduction

You can and should cross-reference sections and sub-sections. We use @steven, and @opendatatorotno

The remainder of this paper is structured as follows. @sec-mydatasection



# Data {#sec-mydatasection}

Some of our data is of Marriages (@fig-marriage), from @opendatatorotno

```{r}
#| label: fig-marriage
#| fig-cap: Marriages in Toronto
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()

```

# Discussion

## First discussion point {#sec-first-point}

The (@fig-marriage) shows the marriages by date across Toronto, using data from @opendatatorotno

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References

